Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-25 doc/PRF2022/PRF_main.tex

\subsection{Mobility problem}
%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
%RJR: In the above sentence, suspection and immersed are redundant 
The Janus particles are suspended in a viscous solvent.
The particles are disks of radius $c$, center $\aa_i$, and
orientation $\theta_i$ relative to the horizontal axis, where $i = 1, \dots, N_b$
and $N_b$ is the number of particles.
The domain $\Omega(t) \subset \mathbb{R}^2$ is the solvent phase and $t$
is time.  The boundary of
$\Omega$ is $\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where
$\Gamma_i$ is the boundary of Janus particle $i$. Assuming inertial
terms are negligible, we have 
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity of the solvent, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
viscosity. The solvent velocity satisfies the no-slip boundary condition
for a rigid body motion
\begin{equation}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{equation}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free conditions.
This means that the force and torque from the hydrodynamic stress on each particle 
are in balance with the total
force and torque coming from the hydrophobic potential and repulsion \cite{Fu2022_JFM}.
To compute this balance, we define
the free energy\cite{Fu2022_JFM}
\begin{equation}
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
where $u(\xx,t)$ is as an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
The parameter $\rho_0$ is an ``effective" distance between particle centers,
below which the steric repulsion between a pair of JPs becomes important.

The order parameter $u(\xx,t)$ is assumed to the minimizer of the free energy $F$ \cite{Fu20}.
Its governing equations $u(\xx,t)$ 
are a screened Laplace equation boundary value problem
as a model for the hydrophobic interaction between water and JPs:
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  \label{eq:SLbc}
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ encodes hydrophobic properties of the
particle-solvent interface.

@@

\subsection{Boundary integral represenation and time stepping}
We recast \eqref{eq:stokes}--\eqref{eq:rigid-vel} and \eqref{eq:SL}
as boundary integral equations (BIEs) and discretize each BIE at
$N$ points on each of the $N_b$ particles with a collocation method.
To express the solution of \eqref{eq:SL},
we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy
, \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL},
$K_0$ is the zeroth-order modified Bessel function of the first kind,
and $\sigma$ is a scalar-valued density function.
The subscript in $\dif s_\yy$ denotes integration with respect to $\yy \in \Gamma$. 
For the velocity, we use the representation [REF]
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
with the vector-valued density function $\eeta$,
Stokeslet 
$\SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + \frac{\rr \otimes \rr}{|\rr|^2}\right)$,
and Rotlet
$\RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$,
$\rr = \xx - \aa_i$ [REF].

>>>>

\subsection{Mobility problem}
%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
%RJR: In the above sentence, suspection and immersed are redundant 
The Janus particles are suspended in a viscous solvent.
The particles are disks of radius $c$, center $\aa_i$, and
orientation $\theta_i$ relative to the horizontal axis, where $i = 1, \dots, N_b$
and $N_b$ is the number of particles.
The domain $\Omega(t) \subset \mathbb{R}^2$ is the solvent phase and $t$
is time.  The boundary of
$\Omega$ is $\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where
$\Gamma_i$ is the boundary of Janus particle $i$. Assuming inertial
terms are negligible, we have 
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity of the solvent, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
viscosity. The solvent velocity satisfies the no-slip boundary condition
for a rigid body motion
\begin{equation}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{equation}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.
Without inertia, the system in~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
also satisfies the force-free and torque-free conditions.
%This means
%that the total force $\FF_i,$ and torque $T_i$ from the hydrodynamic
%stress on each particle (with subscript `$i$') balance the force and
%torque from the hydrophobic potential~\cite{Fu2022_JFM}. 
The total force
and torque from the fluid flow are
\begin{align}
  \label{eq:force}
 \FF_i = \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s, \quad
 T_i = \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
  (\ssigma \cdot \nnu_i) \, \dif s,
  \quad i=1,\ldots,N_b,
\end{align}
respectively, where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu +
\nabla \uu^T \right)$ is the hydrodynamic stress tensor (pressure
tensor), and $\nnu_i$ is the unit outward normal on the $i$th particle.

The total force $\FF_i,$ and torque $T_i$ from the hydrodynamic
stress on each particle (with subscript `$i$') balance the force and
torque from the hydrophobic potential. 
%$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
%particles and the viscous solvent. 
As in~\citet{Fu2022_JFM} such a hydrophobic attraction potential
$u(\xx,t)$ is assumed to the minimizer of the free energy
\begin{align}
=======
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free conditions.
This means that the force and torque from the hydrodynamic stress on each particle 
are in balance with the total
force and torque coming from the hydrophobic potential and repulsion \cite{Fu2022_JFM}.
To compute this balance, we define
the free energy\cite{Fu2022_JFM}
\begin{equation}
>>>>>>> e6ff8abf65732bc50432a8d6cd9352c76cb936ca
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
where $u(\xx,t)$ is as an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
$c$ is an ``effective" distance between particle centers, below which the steric repulsion between a pair of JPs becomes important.
In the followings we let $c$ be the radius of each JP.

The governing equation for $u(\xx,t)$ is obtained by computing the
domain variation of the free energy $F$~\cite{Fu20}. We obtain a
screened Laplace equation boundary value problem as a model for the
hydrophobic interaction between water and JPs:
\begin{alignat}{3}
  \label{eq:SLpde}
  -\rho^2 \Delta u + u &= 0,\qquad &&\xx \in \Omega, \\
  \label{eq:SLbc}
  u &= g, &&\xx \in \bd\Omega, \\
  \label{eq:SLfarfield}
  u &\rightarrow 0, &&|\xx| \rightarrow \infty,
\end{alignat}
where the boundary condition $g$ gives the degree of hydrophobicity the
=======
The parameter $\rho_0$ is an ``effective" distance between particle centers,
below which the steric repulsion between a pair of JPs becomes important.

The order parameter $u(\xx,t)$ is assumed to the minimizer of the free energy $F$ \cite{Fu20}.
Its governing equations $u(\xx,t)$ 
are a screened Laplace equation boundary value problem
as a model for the hydrophobic interaction between water and JPs:
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  \label{eq:SLbc}
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ encodes hydrophobic properties of the
>>>>>>> e6ff8abf65732bc50432a8d6cd9352c76cb936ca
particle-solvent interface.

@@

\subsection{Boundary integral represenation and time stepping}
We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
and~\eqref{eq:SLpde}--\eqref{eq:SLfarfield} as boundary integral
equations (BIEs) and discretize each BIE at $N$ points on each of the
$N_b$ particles with a collocation method. To express the solution
of~\eqref{eq:SLpde}--\eqref{eq:SLfarfield}, we adopt the double layer
potential
\begin{align}
\label{eq:SL_BIE}
  u({\xx}) = \DD[\sigma](\xx) = \int_\Gamma 
    \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, 
    \dif s_\yy, \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
solution to the screened Laplace equation~\eqref{eq:SLpde}, $K_0$ is the
zeroth-order modified Bessel function of the first kind, and $\sigma$ is
a scalar-valued density function.  The subscript in $\dif s_\yy$ denotes
integration with respect to $\yy \in \Gamma$.  For the velocity, we use
the representation~\cite{pow-mir1987}
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
with the vector-valued density function $\eeta$, Stokeslet
$\SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + \frac{\rr
\otimes \rr}{|\rr|^2}\right)$, and Rotlet $\RR(\xx,\aa_i) =
\frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$, $\rr = \xx - \aa_i$.
